Phylogenetics and the human microbiome.

### 2013-09-30 sbreview.tex
Adding funkhouser2013mom reference.
H/T @phylogenomics.

Diversity preservation is of interest for microbiome researchers like it is for eukaryotic organisms, but has not received the formalization and algorithmic treatment surrounding phylogenetic diversity for larger organisms \citep{hartmann2006maximizing,pardi2007resource}.
Martin Blaser in particular has argued that changes in our microbiomes are leading to an increase in autoimmune disease and certain types of cancer \citep[reviewed in][]{cho2012human} and has made passionate appeals to preserve microbiome diversity \citep{blaser2011antibiotic}.
% Indeed, studies show that the modern lifestyle, including antibiotic use, has led to significant changes in microbiome.
Because microbiomes are seeded from mother to child, there is a somewhat equivalent notion of extinction of microbiome when the chain is interrupted.
Consequently, \citet{yatsunenko2012human} have explicitly contrasted microbiome development in urban, forest-dwelling, and rural populations, while \citet{tito2012insights} have endeavored to characterize the microbiome from ancient feces.
How might phylogenetic methods be used in these preservation efforts?

>>>>

Diversity preservation is of interest for microbiome researchers like it is for eukaryotic organisms, but has not received the formalization and algorithmic treatment surrounding phylogenetic diversity for larger organisms \citep{hartmann2006maximizing,pardi2007resource}.
Martin Blaser in particular has argued that changes in our microbiomes are leading to an increase in autoimmune disease and certain types of cancer \citep[reviewed in][]{cho2012human} and has made passionate appeals to preserve microbiome diversity \citep{blaser2011antibiotic}.
% Indeed, studies show that the modern lifestyle, including antibiotic use, has led to significant changes in microbiome.
Because a child's initial microbiome is transmitted from the mother \citep[reviewed in][]{funkhouser2013mom}, there is a somewhat equivalent notion of extinction of microbiome when the chain is interrupted.
Consequently, \citet{yatsunenko2012human} have explicitly contrasted microbiome development in urban, forest-dwelling, and rural populations, while \citet{tito2012insights} have endeavored to characterize the microbiome from ancient feces.
How might phylogenetic methods be used in these preservation efforts?
